### 2020-11-10 thesis/chap_1.tex
re comment

%[we are building on past work]
This work is the continuation of recent research efforts on the connectivity of the region: \cite{albert_applying_2017} and \citep{rayfield_priorisation_2018}. In a seminal paper, \cite{albert_applying_2017} laid out some of the methodological steps we follow such as umbrella species selection and habitat suitability analysis. They also included a simple land use change model that was parameterized to replicate plausible change in the region. \cite{meurant_selecting_2018} developed the criteria for reducing the number of focal species from fourteen to five. They showed that because species had redundant connectivity needs, modelling the needs for 5 species resulted in qualitatively similar results than when modelling the needs of all 14 species, such as in Albert et al. (\citeyear{albert_applying_2017}). While Rayfield et al. (\citeyear{rayfield_priorisation_2018}) extended the spatial scale of the analysis to include the Saint Lawrence lowlands ecoregion, they demonstrated that we could exploit this redundancy to reduce the computing time needed for the connectivity analysis. This is an important development because land use change simulations are also computationally intensive.

@@

The species selection process is unchanged from \cite{rayfield_priorisation_2018}. The species are the Northern short-tailed Shrew (\textit{Blarina brevicauda}), the American marten (\textit{Martes americana}), the Red-Backed Salamander (\textit{Plethodon cinereus}), the Wood Frog (\textit{Rana sylvatica}), and the Black Bear (\textit{Ursus americanus}). As previusly mentionned, these  species are considered umbrella species from the standpoint of ecological connectivity, as it has been shown that modeling the connectivity needs of those 5 species was equivalent to modeling the needs of 14 species in the study region \citep{meurant_selecting_2018, albert_applying_2017}\\

>>>>

%[we are building on past work]
This work is the continuation of recent research efforts on the connectivity of the region: \cite{albert_applying_2017} and \citep{rayfield_priorisation_2018}. In a seminal paper, \cite{albert_applying_2017} laid out some of the methodological steps we follow such as umbrella species selection and habitat suitability analysis. They also included a simple land use change model that was parameterized to replicate plausible change in the region. \cite{meurant_selecting_2018} developed the criteria for reducing the number of focal species from fourteen to five. They showed that because species had redundant connectivity needs, modelling the needs for 5 species resulted in qualitatively similar results than when modelling the needs of all 14 species, such as in \cite{albert_applying_2017}. While Rayfield et al. (\citeyear{rayfield_priorisation_2018}) extended the spatial scale of the analysis to include the Saint Lawrence lowlands ecoregion, they demonstrated that we could exploit this redundancy to reduce the computing time needed for the connectivity analysis. This is an important development because land use change simulations are also computationally intensive.

@@

The species selection process is unchanged from \cite{rayfield_priorisation_2018}. The species are the Northern short-tailed Shrew (\textit{Blarina brevicauda}), the American marten (\textit{Martes americana}), the Red-Backed Salamander (\textit{Plethodon cinereus}), the Wood Frog (\textit{Rana sylvatica}), and the Black Bear (\textit{Ursus americanus}). As previusly mentionned, these  species are considered umbrella species from the standpoint of ecological connectivity in the region, as it has been shown that modeling the connectivity needs of those 5 species was equivalent to modeling the needs of 14 species in the study region \citep{meurant_selecting_2018, albert_applying_2017}. We now give a short description of these 5 species, adapted from \cite{albert_applying_2017}.

The Northern short-tailed Shrew is an abundant small fossorial mammal, mainly found in deciduous and mixed old forests with thick understories. It is generally a poor disperser. The American marten is a small vagile carnivorous predator, found in core areas of dense and old coniferous or mixed forests. It requires large home ranges and generally avoids large openings and clearings, but crosses roads easily. The red-backed salamander is a sedentary and territorial amphibian that favors mature and moist deciduous and mixed forests. It is a poor disperser. The wood frog is a forest-specialist amphibian. It prefers mixed and coniferous stands with closed canopy and moist soil. This poor disperser is particularly sensitive to roads and habitat loss. The black bear is a large opportunistic omnivorous mammal. It likes deciduous and mixed mature forest with dense cover interspersed with small clearings. It is an good disperser as it can travel long distances. It clearly avoids human activity and roads.\\
